% Adapted from http://www.cv-templates.info/2009/10/classicthesis-currvita-latex-cv-template/

\documentclass{scrartcl}        % classe article di KOMA

\makeatletter
\let\saved@bibitem\@bibitem
\makeatother

\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
\usepackage[LabelsAligned]{currvita}    % un buon pacchetto per CV
%\usepackage[eulermath,nochapters]{classicthesis} % stile ClassicThesis
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage{url}        % per gli indirizzi Internet
%\usepackage{cite}
\usepackage{natbib}
\usepackage{bibentry}
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
\date{February 25th, 2011}

%Setup hyperref package, and colours for links, text and headings

\usepackage{hyperref}           

\hypersetup{colorlinks,breaklinks, urlcolor=Maroon,linkcolor=Maroon,
  pdfauthor = {Evan K. Friis},
  pdftitle = {Curriculum Vitae},
}
%\usepackage{eurosym}
\newlength{\datebox}\settowidth{\datebox}{Summer 2007}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3%
\vspace{0.5em}}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}
\newcommand{\Sep}{\vspace{2em}}

\begin{document}

\thispagestyle{empty}
\begin{cv}{\spacedallcaps{Evan Klose Friis}}
%\vspace{1.5em}
%\spacedlowsmallcaps{Personal Data}
\vspace{0.5em}
\hangindent=2em
~\\
Rue de Peupliers 12\\
1205 Gen\`{e}ve\\
Switzerland\\
\href{mailto:friis@physics.ucdavis.edu}{friis@physics.ucdavis.edu} \\
+1 (530) 207-0353

\vspace{1.5em}
\noindent\spacedlowsmallcaps{Research Interests}
\vspace{0.5em}

The bulk of my previous research has concerned development of new experimental
techniques using $\tau$ leptons and their application in searches for the MSSM
Higgs boson. The use of these techniques has dramatically enhanced the
sensitivity of the CMS MSSM Higgs analysis.  In the future, I plan to extend the
number of channels in the MSSM case analysis and apply these techniques in other
Higgs searches using $\tau$s (like the Standard Model), with the goal of setting
the world's best limits (or discovering) the Higgs with the 2011 and 2012 LHC
data.  There are a number of potential improvements to these methods that I am
interested in implementing.  An improvement in either of these methods
translates directly to increased Higgs sensitivity in current and future
datasets.  I am also interested in the utilization of tracking detector
information when identifying and reconstructing $\tau$s.  Finally, I would like
to become involved in developing future detectors, particularly silicon tracking
systems.  I have previous experience in electronics and embedded systems
development, and would like to develop these skills and contribute to a hardware
design project. 

\vspace{1.5em}
\noindent\spacedlowsmallcaps{Education}
\vspace{0.5em}

\NewWorkExperience{June 2011 Est.}{University of California,}{Davis}

\Description{\MarginDate{Ph.D. Experimental High Energy Physics} 
Thesis: ``Search for Higgs bosons decaying to $\tau$ leptons at $\sqrt s = 7$ TeV'' 
Member of the Compact Muon Solenoid (CMS) collaboration at CERN~(2005--Present).
\newline Advisor: Professor~John~\textsc{Conway} }

\Sep

\NewWorkExperience{June 2005}{University of California,}{San Diego}

\Description{\MarginDate{B.S. Physics} Research experience: Non-neutral positron
plasma physics}

\vspace{1.5em}
\spacedlowsmallcaps{Research Experience}
\vspace{0.5em}

\NewWorkExperience{2009-Present}{Higgs Group,}{CMS}

\Description{\MarginDate{Higgs physics} Performed analysis searching for Minimal
Super Symmetric Model (MSSM) Higgs bosons in the $H \rightarrow \tau\tau
\rightarrow \mu + \tau_{\rm{hadrons}}$ channel.  
Set new exclusion limits on the MSSM with 36~pb$^-1$ of 2010 CMS data. 
Authored the ``Secondary Vertex Fit,''
a novel algorithm for reconstructing the invisible energy in $\tau$~lepton
events that dramatically improves kinematic resolution and event acceptance.
The Secondary Vertex Fit method improves the MSSM $\tan\beta$ exclusion limit by 
20\%, pushing the CMS result past the current Tevatron limit. } \Sep 

\NewWorkExperience{2009-Present}{Electroweak Tau Group,}{CMS}

\Description{\MarginDate{$\tau$ physics} 
Measured $Z\rightarrow\tau\tau$ cross section using the 2010 CMS data set.
Developed methods and software for data--driven estimation of backgrounds from
hadronic jet mis--tags in $\tau$ lepton analyses.  } \Sep

\NewWorkExperience{2006-Present}{Tau Physics Object Group,}{CMS}

\Description{\MarginDate{$\tau$ identification} Developed the ``Tau Neural
Classifier'' tau identification algorithm, which has jet mis--tag rate that is a
factor of five lower than the previous algorithm used in CMS.
Measured the hadronic jet mis--tag rate from first 7 TeV
CMS datasets.  Currently serve as software librarian and liaison to CMS
reconstruction software group.} \Sep

\NewWorkExperience{2010-Present}{Luminous region monitoring at}{CMS}

\Description{\MarginDate{Beamspot}Developed and supported tools to measure and
monitor the luminous collision region at the CMS experiment.} \Sep

\NewWorkExperience{2007-2008}{Pixel Detector Calibrations,}{CMS}

\Description{\MarginDate{Pixel Detector}Designed and developed software to measure the gain,
noise, and thresholds of the sixty million channels of the CMS silicon pixel detector.
Developed data formats and tools to store calibration results in the CMS
conditions database.
} 

\vspace{1.5em}
\spacedlowsmallcaps{Awards and Honors}
\vspace{0.5em}

\Description{\MarginDate{Spring 2009} Visiting Scholar, Scuola Normale Superiore, Pisa,
Italy}
\vspace{1em}
\Description{\MarginDate{2005, 2009} UC Davis Block Grant Recipient}
\vspace{1em}
\Description{\MarginDate{2006-2007, 2009} UC Davis GAANN Fellow}

\vspace{1.5em}
\spacedlowsmallcaps{Teaching}
\vspace{0.5em}

\Description{\MarginDate{January 2010} Workshop Facilitator, EJTERM 2010, Fermi
National Laboratory}
\vspace{1em}
\Description{\MarginDate{Five quarters} UC Davis Physics 116
Electronics Lab Assistant - assisted in developing new curriculum using modern
microcontrollers.}
\vspace{1em}
\Description{\MarginDate{Three quarters} UC Davis General Physics (7/9)}
\vspace{1em}

\vspace{1.5em}
\spacedlowsmallcaps{Invited Talks}
\vspace{0.5em}

\Description{\MarginDate{September 2010} ``Tau reconstruction and identification
in CMS'', 11th International Workshop on Tau Lepton Physics, Manchester, United
Kingdom}
\vspace{1em}
\Description{\MarginDate{May 2010} ``Tau ID Object Performance '', US CMS 
Collaboration Meeting, Brown University, Providence, Rhode Island}

\vspace{1.5em}
\spacedlowsmallcaps{Publications}
\vspace{0.5em}

\Description{See attached list.}

\begingroup
\makeatletter
\let\@bibitem\saved@bibitem
\bibliographystyle{amsplain} 
\nobibliography{spires_papers}
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
%\Description{\bibentry{:2009ft}}
%\Description{\bibentry{:2009hw}}
%\Description{\bibentry{Chatrchyan:2009hg}}
% Just generate all the bibliography
\nocite{*}
\endgroup

\enlargethispage{\baselineskip}
\end{cv}
\end{document}
