\documentclass[12pt]{amsart}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
\usepackage{currvita}
\usepackage{cite}
\usepackage{bibentry}
% See the ``Article customise'' template for come common customisations

\title{}
\author{}
\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}
\nobibliography*
\begin{cv}{Curriculum Vitae}

\begin{cvlist}{Personal Data}
\item Evan K. Friis\\
Rue de Peupliers 12
1205 Gen\`{e}ve\\

\item Tel. +1 (530) 207-0353\\
Email. friis@physics.ucdavis.edu
\end{cvlist}

\begin{cvlist}{Education}
\item[Ph.D. 2011 Est.] University of California, Davis, Experimental High Energy Physics 
   ``Search for Higgs bosons decaying to $\tau$ leptons at $\sqrt s = 10$TeV'' Thesis advisor: John Conway
\item[B.S. 2005] University of California, San Diego, Physics
\end{cvlist}

\begin{cvlist}{Research Experience}
\item[6/2009 - Present] CMS Electroweak Tau Physics group - Developed methods and software to measure $\tau$ identification background rates from data.
\item[1/2009 - Present] Tau-ID liaison to Reconstruction Committee - Managed tau-ID software developers and coordinated with CMS collaboration.
\item[6/2006 - Present] Compact Muon Solenoid (CMS) Tau-ID Group - Developed and optimized algorithms to identify and reconstruct $\tau$ leptons at hadron colliders.
\item[8/2007 - 6/2008] CMS Pixel Detector Commissioning Group - Designed and implemented software to characterize and calibrate the 60 million channels in the CMS pixel detector.
\item[9/2004 - 8/2005] Surko Plasma Physics Group (UCSD) - Developed high-speed control system for non-neutral positron plasma trap.
\item[6/2004 - 8/2004] Princeton Plasma Physics Lab - Developed test stand for simulating large, high-frequency pressure variations found in pulsed excimer lasers.
\end{cvlist}

\begin{cvlist}{Teaching Experience}
\item[January 5-9, 2010] Workshop Facilitator, EJTERM 2010, Fermi National Laboratory
\item[F06, FW08, F09] UC Davis Physics 116A Electronics Lab Assistant -
   assisted in developing new curriculum using modern microcontrollers.
\item[W06, S06] UC Davis Physics 9A General Physics Lab Assistant
\item[F05] UC Davis Physics 7B General Physics Discussion/Lab TA
\end{cvlist}

\begin{cvlist}{Publications}
\item
   \bibentry{:2008zzk}
\item 
   \bibentry{Chatrchyan:2009si}
\item
   \bibentry{Friis:2008tg}
\item
   \bibentry{CMS-PAS-PFT-08-001}
\item
   \bibentry{2004APS..DPPFP1051F}
\end{cvlist}

\begin{cvlist}{Awards}
\item Visiting Scholar, Scuola Normale Superiore, Pisa, Italy, Spring 2009
\item UC Davis Block Grant Recipient, 2005, Spring 2009
\item UC Davis GAANN Fellow, 2006-2007, Winter 2010 
\end{cvlist}
\end{cv}

\bibliographystyle{plain} 
\nobibliography{my_papers.bib}
\end{document}
