% Adapted from http://www.cv-templates.info/2009/10/classicthesis-currvita-latex-cv-template/

\documentclass{scrartcl}        % classe article di KOMA

\makeatletter
%\let\saved@bibitem\@bibitem
\makeatother

\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
\usepackage[LabelsAligned]{currvita}    % un buon pacchetto per CV
%\usepackage[eulermath,nochapters]{classicthesis} % stile ClassicThesis
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage{url}        % per gli indirizzi Internet
%\usepackage{cite}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{fullpage}
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
\date{}
%\date{October 10th, 2010}
%\date{}

%Setup hyperref package, and colours for links, text and headings

\usepackage{hyperref}           

\hypersetup{colorlinks,breaklinks, urlcolor=Maroon,linkcolor=Maroon,
  pdfauthor = {Evan K. Friis},
  pdftitle = {Statement of Research Interest},
}
%\usepackage{eurosym}
\newlength{\datebox}\settowidth{\datebox}{Summer 2007}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3%
\vspace{0.5em}}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}
\newcommand{\Sep}{\vspace{2em}}
\newcommand{\TeV}{\mathrm{Te\hspace{-.08em}V}}
\frenchspacing

\begin{document}

\thispagestyle{empty}
\begin{cv}{\spacedallcaps{Statement of Research Interest}}
\Sep

%Outline:
%Past work:
  %Searches for the MSSM Higgs boson
    %Higgs boson <-- mass
    %MSSM <-- solve hierarchy problem, dark matter candidate
  %Main contributions are novel algorithms
    %Tau ID
    %SV fit
  %Developed reconstruction techniques and software to measure backgrounds.
  %Set worlds best limits on MSSM in 2010
  %Expect even better results in 2011

%Future work:
  %Interested in working on more hardware development
  %Would like to be involved with the development of an experiment

%Interested in the neutrino sector
  %Indirect measurements are amusing
  %Neutrino mass and oscillations first real deviations from SM

My graduate career research has centered on the use of tau leptons as a probe of
new physics at the Compact Muon Solenoid (CMS) experiment.  The tau lepton is
particularly useful for searching for Higgs bosons.  The Higgs boson is a
particle hypothesized to exist in the Standard Model as the catalyst of the
mechanism that would impart mass to the particles that form our natural world.
If it exists, the Higgs boson ``couples'' to mass, which means that it prefers
to decay to pairs of the heaviest possible particle.  As the heaviest lepton,
the tau provides one of the cleanest signatures to look for the Higgs.  The tau
is even more important in the context of the Minimal SuperSymmetric Model
(MSSM), a promising extension to the Standard Model.  In the MSSM, the Higgs
coupling to the tau is enhanced by the model parameter $\tan\beta$; the
$H\to\tau\tau$ channel is sensitive over the entire mass range of the MSSM
Higgs. 

While the tau enjoys many phenomenological advantages, in practice tau leptons
pose many experimental challenges.  First, they are hard to find.  The tau
lepton always decays before detection, and the
majority of taus decay ``hadronically.'' Hadronic decays consist of collimated
low multiplicity sprays of pions that look very similar to
the quark and gluon jets which are produced at rates many orders of magnitude
($\approx 10^8$) higher than signals of interest.  An analysis using tau leptons
therefore requires a robust tau identification strategy to avoid being
overwhelmed by misidentified quark and gluon jets.  Once found, tau leptons
present a second challenge: a tau decay always includes one or two neutrinos, so
only a fraction of the original energy of the tau is reconstructed in the
detector.  The only experimental signature of the neutrinos is an overall low
resolution imbalance in the transverse momentum of the event.  This makes
hunting for new physics bumps difficult, as the kinematic distributions of the
visible tau decay products are smeared due to the unknown neutrino momentum.

I enjoy creating innovative methods that make measurements thought to be
unfeasible, possible.  Over the course of my graduate career I have developed
innovative techniques to address both the ``hard to find'' and ``hard to
measure'' tau lepton challenges.  To find taus, I developed a new tau
identification algorithm called the ``Tau Neural Classifier''~(TaNC).  The
method uses an ensemble of neural networks and reconstructs the different
hadronic decay modes of the tau.  The TaNC algorithm reduced the background
misidentification rate of the previous algorithm used in CMS analyses by a
factor of five while maintaining the same efficiency to identify real taus.  To
address the ``hard to measure'' problem, I developed the Secondary Vertex (SV)
fit.  The SVfit algorithm uses a likelihood maximization technique to
reconstruct the momenta of neutrinos associated to tau decays in an event.  The
SVfit allows the \emph{full} tau pair invariant mass to be reconstructed in each
event. The tau pair mass is the most natural and sensitive observable to
the presence of a new particle.

The culmination of these developments is the result from the Compact Muon
Solenoid experiment (recently accepted for publication in Phys.  Rev. Lett. B)
which set the world's best limits on a direct search for the MSSM Higgs.  I was
a major contributor to the analysis methods, measurements of the backgrounds,
and systematic error determination in the $H \to \mu \tau_{\mathrm{hadrons}}$
channel, in which one of the tau leptons decays to a muon and two neutrinos, and
the other tau lepton decays to hadrons and one neutrino.  The SVfit method was
used in all channels of the analysis, and improved the limit on the MSSM
$\tan\beta$ parameter by 20\%.  The improvements provided by the new tau
identification and the SVfit allowed CMS to beat the Tevatron MSSM limit with
one third of the data thought to be necessary.  I also contributed to the
related measurement of the Standard Model $Z\to\tau\tau$ cross section. The
precision of the CMS $Z\to\tau\tau$ cross section measurement rivals that of the
D\O~experiment using only $1/30$th of the data. 

Over the next few months, my research plans include improving the CMS SVfit and
tau identification algorithms and updating the MSSM Higgs search using the
2011~CMS dataset.  Additionally, the SVfit code has been generalized to
operate on an arbitrary number of a taus and I will support other groups in
applying it to other Higgs searches.  

As a postdoc, I will continue to creatively contribute to the scientific
community. I plan to increase the impact and scope of my contributions by
obtaining leadership roles and mentoring younger scientists; increasing the
technical diversity of my work; and working on new types of physics analyses.

I intend to play a leadership role in collaborations I am a member of. From my
experience at CERN I have gained an understanding of the requisite elements of
productive scientific collaboration and become adept at communication and
teamwork. Over the past three years, I have successfully managed the
development of the CMS tau software, coordinating the efforts of a diversity of
developers and acting as liaison to the CMS software management.  The CMS tau
software was shown to outperform the ATLAS tau ID by a factor of four at the Tau
2010 conference. 

I would like to be involved with a larger cross section of experimental
activities.  In particular, I want to become involved in hardware work and the
development of future detectors. I have a solid grounding in electronics and
embedded development. I began my undergraduate studies as an electrical engineer
before switching to physics, taught the UC Davis physics electronics lab, and
enjoy electronics as a hobby.  I also have mechanical design and construction
experience from my undergraduate work the Princeton Plasma Lab and the Scripps
Institute of Oceanography. I plan to develop and apply these skills in solving
experimental physics problems.

\textbf{[Next paragraph only for Neutrino physics]}

Scientifically, I am very interested in conducting research in neutrino and
particle astrophysics. Having worked on the largest experiment in the world, I
am interested in working on smaller experiments in order to contribute in a more
holistic and interdisciplinary manner. Further, the presence of neutrino mass on
a scale far \emph{below} the electroweak scale is a very interesting problem.
The effect is known to be there; like Cavendish's measurement of $G$, the
neutrino mass challenges us to refine and improve the precision of our
techniques to enable measurement. Neutrino mass, oscillations, and the presence
of dark matter are discoveries which have exposed a crack in the carapace of the
Standard Model.  I want to build precision experimental techniques and
innovative analyses to lever the crack open and peer inside.

\textbf{[Next paragraph only for CMS physics]}

Scientifically, I intend to continue to work on analyses searching for new
physics at CMS\@.  There are a number of exciting searches to be done 
using taus.  The measurement of the $Z\to\tau\tau$ cross section and the MSSM
Higgs search have demonstrated that taus are well understood at CMS, and can
be used with confidence.  The tau channel will play an important role in
discovering or ruling out the Standard Model Higgs near the LEP limit, and is an
important probe of SUSY and exotic physics. While I am interested in continuing
my expertise with taus, I am equally interested in exploring opportunities with
other final state particles.  Over the next two years, the high rate of data
provided by the LHC will enable scientists to address many long standing
questions about nature. I plan to help answer them. 

\end{cv}
\end{document}
